Person with advantage functionality for `hyper3` objects: `pwa3()`

### 2025-12-07 inst/pwa3.Rmd
another case study

@@

```{r plotlamf, echo=TRUE,fig.cap="Log-likelihood function for lambda"}
plot(log(l), like - optimal_sol$objective,
	     type='b', pch=16,
	     xlab = expression(log(lambda)),
	     ylab = "log-likelihood")
abline(h = c(0, -2))
abline(v = log(optimal_sol$maximum))
abline(v = 0)
segments(x0 = log(c(lower$root, upper$root)), y0 = -2.25, y1 = -1.75, col='gray')
```

@@

>>>>

```{r out.width='20%', out.extra='style="float:right; padding:10px"',echo=FALSE}
knitr::include_graphics(system.file("help/figures/hyper2.png", package = "hyper2"))
```

<font size="1"> (takes about five minutes to run without cache)
</font>

@@

```{r plotlamf, echo=TRUE,fig.cap="Log-likelihood function for lambda"}
plot(log(l), like - optimal_sol$objective,
	     type='b', pch=16,
	     xlab = expression(log(lambda)),
	     ylab = "log-likelihood")
abline(h = c(0, -2), col='gray')
abline(v = log(optimal_sol$maximum))
abline(v = 0, lty=2)
segments(x0 = log(c(lower$root, upper$root)), y0 = -2.25, y1 = -1.75, col='gray')
```

@@

# Another example {-}

In this case, competitor `a` receives help $\lambda$ or $\lambda^n$ if
he gets $n$ sets of help.  Below, in function `lam2()` we see that, in
general, the more help `a` gets, the better he does.  See how a
negative power corresponds to some sort of hindrance or penalty, and a
zero power (of course) corresponds to no help at all.

```{r lam2def}
lam2 <- function(lam){

  race_help <- 
    race(c("d","c","a","b")) |> pwa3(a = lam^0 ) +
    race(c("c","b","d","a")) |> pwa3(a = lam^-3) + 
    race(c("c","b","d","a")) |> pwa3(a = lam^-2) + 
    race(c("c","b","a","d")) |> pwa3(a = lam^-1) + 
    race(c("a","c","b","d")) |> pwa3(a = lam   ) + 
    race(c("a","c","b","d")) |> pwa3(a = lam^3 ) +
    race(c("a","b","d","c")) |> pwa3(a = lam   ) +
    race(c("c","a","d","b")) |> pwa3(a = lam^2 )

    maxp(race_help, give=TRUE)$value
}
```

```{r calclam2f, cache=TRUE}
l <- exp(seq(from=log(0.8), to=log(19.1), len=11))
like2 <- sapply(l,lam2)
```

```{r}
plot(log(l),like2-max(like2),type="b",pch=16)
abline(h=c(0,-2), col='gray')
abline(v=0, lty=2)
```

# Another other example {-}

In this example we see help being given to two competitors at the same
time.

```{r lam3def}

myr <- function(a1,a2,a3,a4,a5){race(letters[c(a1,a2,a3,a4,a5)])}

lam3 <- function(l){
  race_help <- 
    myr(3,1,2,4,5) |> pwa3(a=l, b=l) + 
    myr(2,3,1,4,5) |> pwa3(a=l, b=l) + 
    myr(3,1,5,4,2) |> pwa3(a=1, b=1) +   # no help!
    myr(4,2,5,3,1) |> pwa3(a=1, b=1) +   # no help!
    myr(3,1,2,4,5) |> pwa3(a=l, b=l)

    maxp(race_help, give=TRUE)$value
}
```

```{r calclam3, cache=TRUE}
l <- exp(seq(from=log(0.5), to=log(84.1), len=13))
like3 <- sapply(l,lam3)
```

```{r plotlam3}
plot(log(l),like3-max(like3), type="b", pch=16)
abline(h=c(0,-2), col='gray')
abline(v=0, lty=2)
```

### References {-}
